Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-26 paper.tex
Acknowledgements fixed CBRAIN

\paragraph{Scalability} Adding a new engine instance requires a new
instance of the science gateway, which is in general not possible
(\texttt{S$_1$}=2). Specific IT setups such as load-balancing between
web server instances might be used to deal with this
issue. \closedanswerednote{Tristan}{What-about load-balancing between web
  server instances?}{Marc-e}{Would that really be considered a real
  architectural feature or an IT hack?}{Tristan}{I agree, we should
  keep IT setups out of the picture. Depending on the internals of the
  science gateway, such hacks may or may not be feasible. I added a
  sentence to mention this possibility, without changing the score.}
Distributed engines are not available by default
(\texttt{S$_2$}=1). The scheduling of tasks on the infrastructure is
as complex as in any other architecture since the workflow engine
might implement any kind of scheduling policy (\texttt{S$_3$}=0).

@@

This work is in the scope of the LABEX PRIMES (ANR-11- LABX-0063) of
Universit\'e de Lyon, within the program ``Investissements d’Avenir''
(ANR-11-IDEX-0007) operated by the French National Research Agency
(ANR). This work also falls into the scope of the scientific topics of
the French National Grid Institute (IdG). We thank the site
administrators of the European Grid Initiative and the GGUS support
for their help related to the VIP platform. We are grateful for the
computing cycles, storage, and support obtained from Compute Canada
(\url{https://computecanada.ca}) for CBRAIN. This work has been made
possible with the support of the Irving Ludmer Family Foundation and
the Ludmer Centre for Neuroinformatics and Mental
Health. \answerednote{Marc-e}{Would it be proper to thank EGI?
  Compute Canada? CANARIE?}{Tristan}{Added EGI and Compute Canada. Not sure if
  Canarie should be added. What about Calcul QC?}

>>>>

\paragraph{Scalability} Adding a new engine instance requires a new
instance of the science gateway, which is in general not possible
(\texttt{S$_1$}=2)\answerednote{Tristan}{What-about load-balancing between web
  server instances?}{Marc-e}{Would that really be considered a
  real architectural feature or an IT hack?}.  Distributed engines are
not available by default (\texttt{S$_2$}=1). The scheduling of tasks
on the infrastructure is as complex as in any other architecture since
the workflow engine might implement any kind of scheduling policy
(\texttt{S$_3$}=0).

@@

This work is in the scope of the LABEX PRIMES (ANR-11- LABX-0063) of
Universit\'e de Lyon, within the program ``Investissements d’Avenir''
(ANR-11-IDEX-0007) operated by the French National Research Agency
(ANR). This work also falls into the scope of the scientific topics of
the French National Grid Institute (IdG). We thank the site
administrators of the European Grid Initiative and the GGUS support
for their help related to the VIP platform. The CBRAIN team is grateful for the
computing cycles, storage, and support obtained from Compute Canada
(\url{https://computecanada.ca}) and platform development program from CANARIE
 (\url{http://www.canarie.ca/}). This work has been made possible with the support of the Irving Ludmer Family Foundation and
the Ludmer Centre for Neuroinformatics and Mental Health. \answerednote{Marc-e}{Would it be proper to thank EGI?
  Compute Canada? CANARIE?}{Tristan}{Added EGI and Compute Canada. Not sure if
  Canarie should be added. What about Calcul QC?}{Marc-e}{CQ, no. CANARIE, I'd
  say yes since they funded a major chunk of CBRAIN's development.}
